Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-04-30 tex/ms.tex
equation formatting

% ---- Hogg (aastex) mode ----
\documentclass[12pt, letterpaper, preprint]{aastex}
% ----

% ---- Charlie (emulateapj) mode ----
% \documentclass[iop,numberedappendix]{emulateapj}
% \usepackage{apjfonts}
% ----

@@

We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} G(\lambda,\sigma_v) \otimes 
S(\lambda, t, Z [, \beta]) e^ {-k_\lambda\tau_V} 
\\ 
\lambda_o & = & (1+z)\lambda 
\\
\theta & \equiv & [m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta]
\quad ,
\end{eqnarray} where the parameters $\theta$ include the stellar mass
$m_*$, effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion $\sigma_v$, luminosity distance $d_L$ and redshift
$z$.  The spectrum of one solar mass of stars that formed at time $t$
with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$ where
the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks
\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
purposes of this exercise, with no loss of generality (KEEPING IMF
SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ to the Milky
way average of \citet{CCM89} and assume that $d_L$ is known to high
precision from independent methods.

@@

We estimate the posterior through MCMC sampling. Our sampling of the
posterior is accomplished using \texttt{emcee} \cite{dfm} after an
intial round of minimization.  \texttt{emcee} is an implementation of
the affine-invariant ensemble sampler of \citet{GW}, and unlike
typical Metropolis-Hastings MCMC sampling does not require the
specification of step sizes in each dimension.  Our prior
distributions are in all cases top-hat functions, though more
informative priors distributions may be used.  Informative priors may
be especially appropriate for the calibration parameters $\alpha$ if
additional information about the instrument is available or for the
parameters of interest $\theta$, for example in the case where there
is knowledge of the metallicity distribution of the population from
which a given cluster is drawn.

NEEDS MASSIVE REWORDING.
In Figure \ref{fig:calibrated_spectrum} we show the spectrum resulting
from draws of the parameters $[\theta,alpha]$ from the posterior
distribution.  This figure also shows the calibrated spectrum on which
the priors were conditioned, and individual components of the model
constructed from each draw.   In Figure \ref{fig:calibrated_residuals}
we show the residuals between the data and the draws from the
posterior, for the spectra and the photometry.

>>>>

% ---- Hogg (aastex) mode ----
%\documentclass[12pt, letterpaper, preprint]{aastex}
% ----

% ---- Charlie (emulateapj) mode ----
 \documentclass[iop,numberedappendix]{emulateapj}
 \usepackage{apjfonts}
% ----

@@

We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma_v) \otimes 
S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V} 
\\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include the stellar mass
$m_*$, effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion $\sigma_v$, luminosity distance $d_L$, and
redshift $z$.  The spectrum of one solar mass of stars that formed at
time $t$ with metallicity $Z$ is given by $S(\lambda, t, Z [, \beta])$
where the additional parameters $\beta$ may include details of the
population synthesis model, such as the IMF slope and adjustments to
the stellar spectra or stellar evolutionary tracks
\citep[e.g.][]{FSPS}. We will assume $\beta$ to be fixed for the
purposes of this exercise, with no loss of generality (KEEPING IMF
SLOPE CONSTANT FOR NOW).  We will also fix the shape of the
attenuation curve, $k_\lambda \equiv \tau_\lambda/\tau_V$ to the Milky
way average of \citet{CCM89} and assume that $d_L$ is known to high
precision from independent methods. (BDJ NOTE TO SELF - do not use $k$
for the attenuation curve shape - will confuse people used to
reddening curves)

@@

We estimate the posterior through MCMC sampling. Our sampling of the
posterior is accomplished using \texttt{emcee} \cite{dfm} after an
intial round of optimization using Powell's method.  \texttt{emcee} is
an implementation of the affine-invariant ensemble sampler of
\citet{GW}, and unlike typical Metropolis-Hastings MCMC sampling does
not require the specification of step sizes in each dimension.  Our
prior distributions are in all cases top-hat functions, though more
informative priors distributions may be used.  Informative priors may
be especially appropriate for the calibration parameters $\alpha$ if
additional information about the instrument is available or for the
parameters of interest $\theta$, for example in the case where there
is knowledge of the metallicity distribution of the population from
which a given cluster is drawn.

NEEDS MASSIVE REWORDING.
In Figure \ref{fig:calibrated_spectrum} we show the spectrum resulting
from draws of the parameters $[\theta,\alpha]$ from the posterior
distribution.  This figure also shows the calibrated spectrum on which
the priors were conditioned, and individual components of the model
constructed from each draw.   In Figure \ref{fig:calibrated_residuals}
we show the residuals between the data and the draws from the
posterior, for the spectra and the photometry.
